A multidimensional approach for measuring meritocratic beliefs with the ISSP social inequality survey: Possibilities, limitations and alternatives

### 2023-09-13 paper-blinded-RR-IJS.Rmd
ajustes tablas

```{r table-indicadores, echo=FALSE}
 if (!require("pacman")) install.packages("pacman")
 # remotes::install_github('haozhu233/kableExtra@a6af5c0')  # for problems with collapse_rows()
 pacman::p_load(knitr, kableExtra, dplyr)
 table_format = if (knitr::is_html_output()) {
   #conditional instructions for kable
   "html" #if html set "html" in format
 } else if (knitr::is_latex_output()) {
   "latex"#if latex set "latex" in format
 }
 tabitems <- read.csv(file = "input/tables/table01.csv",header = 1,sep = ",",encoding = "UTF-8") # call file  generated externally for the table
 cnames <- c("Component", "Dimensions","Item (English)" , "Item original (Spanish)")
 cap <- "Items of the perceptions and preferences for meritocracy scale."

 knitr::kable(tabitems, table_format, booktabs = T, linesep = "",col.names = cnames, caption = cap) %>%
   kableExtra::kable_styling(
     full_width = T,
     latex_options = c("hold_position"),
     position = "center",
     font_size = 10,
     bootstrap_options=c("striped", "bordered")) %>%
   kableExtra::column_spec(column = 1, width = "1.5cm", ) %>%
   kableExtra::column_spec(column = 2,width = "2 cm") %>%
   kableExtra::collapse_rows(columns = 1:2,valign = "middle")
```

>>>>

```{r table-indicadores, echo=FALSE}
 if (!require("pacman")) install.packages("pacman")
 # remotes::install_github('haozhu233/kableExtra@a6af5c0')  # for problems with collapse_rows()
 pacman::p_load(knitr, kableExtra, dplyr)
 table_format = if (knitr::is_html_output()) {
   #conditional instructions for kable
   "html" #if html set "html" in format
 } else if (knitr::is_latex_output()) {
   "latex"#if latex set "latex" in format
 }
 tabitems <- read.csv(file = "input/tables/table01.csv",header = 1,sep = ",",encoding = "UTF-8") # call file  generated externally for the table
 tabitems$itemsspa <- NULL
 tabitems$issp <- c("How important is hard work?","-",
                    "How important is coming from a wealthy family?", "How important is knowing the right people",
                    "How hard he or she works at the job?*","How well he or she does the job?*",
                    "-", "-")
 cnames <- c("Component", "Dimensions","Items" , "Items ISSP (2009,2019)")
 cap <- "Items' battery for the multidimensional measurement of meritocratic beliefs and their equivalents in ISSP"
 knitr::kable(tabitems, table_format, booktabs = T, linesep = "",col.names = cnames, caption = cap) %>%
   kableExtra::kable_styling(
     full_width = T,
     latex_options = c("hold_position"),
     position = "center",
     font_size = 10,
     bootstrap_options=c("striped", "bordered")) %>%
   kableExtra::column_spec(column = 1, width = "1.5cm", ) %>%
   kableExtra::column_spec(column = 2,width = "2 cm") %>%
   kableExtra::collapse_rows(columns = 1:2,valign = "middle") %>%
   kableExtra::footnote(general = "Those with an asterisk (*) are only present in 2009",footnote_as_chunk = T)
```
\pagebreak
